\section{Introduction} \label{sec:intro}
\textbf{Points to mention}
\begin{itemize}
    \item my own contribution: 
    \begin{enumerate}
        \item improved methodology to detect and estimate heterogeneity 
        \item two-stage approach in which we model treatment as function of observables allows to reduce noise from other variables, no need to only use dummy variable but can use true quantity 
        \item testing whether households are actually different from ATE, i.e. whether heterogeneity is significant 
        \item improve on capturing the actual effect of rebate receival
        \item can determine the actual influence of single variables on a better level than just correlation (PDP and ICE)
    \end{enumerate}
    \item focus more on policy maker view and why it's crucial to understand responses
    \item conditional Treatment Effect is of first-order importance for policy makers as in other settings more targeted transfers might be suitable and it's important to understand what people spend their transfer on (analysing the different good categories) $\rightarrow$ compare TE for differen sub-categories for same subset of households (e.g. bottom 20 in total reaction to see how their reaction splits up)
\end{itemize}

How do households respond to income shocks and how do their responses differ given their personal characteristics and economic circumstances? These questions are not only at the centre of a wide academic debate in economics but also of major importance for policy makers. While the former revolves around verifying or neglecting baseline economic theories such as the Permanent Income Hypothesis (PIH), the latter are interested in improving targeted transfers to more efficiently use government funds. These two sides have sparked many investigations using different approaches (a wide array of approaches) to quantify the marginal propensity to consume (MPC) out of income shocks. The MPC - at the centre of macroeconomics since Keynes introduced it at the heart of his General Economic Theory - quantifies how much households will spend on consumption of each dollar they receive from an income shock. While research has long focused on quantifying whether the MPC out of income shocks is zero and thus in line with the PIH, the literature has seen a shift of focus over the last decade. On average most studies support the notion of a zero MPC, however, more recent evidence suggests that for specific groups the response is significantly different. \\
Empirical research related to the MPC and its heterogeneity has used several settings to identify income shocks. One of the most prominent is to use natural experiments in which households receive non-targeted stimulus payments from the government. Following \cite{parker_etal_13} and \cite{ms_14}, we exploit the 2008 tax rebate in the USA to estimate households' MPC using data collected by the Consumer Expenditure Survey. Similar to these two prior studies, we are able to use the rich information on consumption the CEX provides to not only identify heterogeneities in the overall MPC but also to analyse which categories of consumption goods households spend their rebate on. However, our econometric approach sets us apart as it is more sophisticated and more precise in detecting heterogeneities compared to any contribution we know of. One major issue in the existing literature is the way how heterogeneity is defined. More precisely, most studies rely on either splitting their sample into smaller sub samples and estimating the MPC within each sample or use dummy variables that are defined by the authors based on some continuous variable. These approaches suffer from the severe issue that any heterogeneity that does not fall into this pre-defined pattern is not captured and will muddy the results of these investigations. In the worst case these procedures can lead to missing any heterogeneity at all or missing patterns within these pre-defined subgroups. On the contrary, our Double Machine Learning (DML) approach allows us to estimate the conditional MPC out of the tax rebate of each individual household. Prior studies have to rely on looking at the correlation between their estimates and characteristics such as liquidity, but our setting enables us to calculate more sophisticated measures that capture the influence of each variable on the MPC. We are not capable of estimating general equilibrium effects due to the design of our study but we relate our findings to the most prominent channels identified as potential drivers of heterogeneity. \\
Namely, the two most prominent channels are life-cycle dynamics and liquidity. The former is driven by a consumer's age and the associated fluctuation in income. As data consistently shows (Attanasio and Weber, 2010), consumption follows a hump shape over the life-cycle. In the case of liquidity, its role is linked to the nature of the income shock and completeness of the credit market. If a positive income shock is anticipated, households that are already close to or at their borrowing constraint cannot borrow new funds to smooth consumption in anticipation of a higher future income. Thus, once the shock realises, we will observe an increase in consumption - although if we follow the PIH, this increase is rather small as the additional income is spread out over all future periods. In case of a negative anticipated shock, saving is always possible for any household and hence we will not see a reaction once the shock realises. E.g. \cite{bunn_etal} document this asymmetry depending on the sign of the shock (\textbf{they document this for unanticipated shocks, shift back}). Thus, more liquid households react less to a positive anticipated shock in comparison with liquidity constrained ones. In contrast, in case of an unanticipated shock, we expect the opposite. Think of an agent that is temporarily out of work and has no liquid wealth at their disposal. In case of a negative shock, the agent is forced to adjust their consumption behaviour downward. Meanwhile, a positive shock will always be saved and stretched over future periods, no matter the level of households' liquidity. However, these theoretical predictions are made within a permanent income framework in which households try to smooth consumption over time. It is important to highlight that in our setting, households experience an anticipated - at least for most - positive income shock. Therefore, following the previous arguments, theory would expect older households to react less, but liquidity not being a major driver. However, the tax rebate was disbursed to US citizens (\textbf{maybe citizens sounds like only those got the rebate, which is not true 100\%}) during a time of national and global economic downturn. Thus, many households receiving the stimulus might have been in economic turmoil when receiving the payment and actually spend it to cover regular expenses that they otherwise would not have been able to cover (e.g. rent or utilities). \\
The fine-grained consumption data of the CEX allows us to identify what kind of goods households consumed and what they spent their stimulus money on. As Kaplan and Violante (2014) note, the tax stimulus is anticiapted and is subject to these special circumstances. Therefore, one might also speak of our estimated coefficients as a 'Propensity to consume the rebate' or 'rebate coeffcient', which is not necessarily equivalent to households' overall MPC. We compare our estimates with the range found in the literature using different income shock sources to get a grasp of whether this difference might play a role and for what households it does. However, while a government stimulus program might not be perfectly appropriate to verify theoretical models concerned with the MPC, providing evidence on their effect on individuals is of major importance for future policy making. While in some cases when economic relief is urgent broadly defined, non-targeted stimuli might be a good option to pursue, targeted transfers can play a major role in many policy settings. \textbf{(rephrase)}\\ 

\textbf{this needs to be implemented somewhere}
By exact definition, the MPC is the reaction to an unanticipated, transitory income shock. However, in out setting, the shock cannot be fully seen as unanticipated as the tax stimulus payment was signed into law and therefore known to the public several months before the payments were conducted. However, in such cases to identify only the contemporaneous reaction of households the empirical literature (e.g. \cite{parker_etal_13}) .  \\ 

\textbf{section on results here}
We show that indeed both these channels play a role in the heterogeneity of households' response to the 2008 tax stimulus. Similar to the existing literature we find... However, additionally we are able to show that the heterogeneity is not only linear/indeed linear... \\ 
The rest of the paper is structured as follows: Section \ref{sec:lit} summarizes the theoretical and empirical literature on MPC heterogeneity. Section \ref{sec:data} discusses the data source and challenges connected with it. The empirical methodology we use is described in Section \ref{sec:methodology}, while Section \ref{sec:estim_res} presents the identification and estimation results. Section \ref{sec:conc} concludes.